A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-29 main.tex
Wrote on transition abstraction and application.

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bcprules, proof}
\usepackage{fancybox}
\usepackage{mathtools}
\usepackage{float}
\usepackage{xparse}
% \usepackage{ebproof}
\usepackage{lscape}
\usepackage{mdframed}

@@

\newcommand{\LTP}{$\lambda^{\triangleright\%}$\ }
\newcommand{\LMD}{$\lambda^{\textrm{MD}}$\ }
\newcommand{\LLF}{$\lambda^{\textrm{LF}}$\ }

@@

In \LTP, quote and unquote are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ when $M$ has $\tau$ type.
The type of $\TBL_\alpha M$ is $\tau$ when $M$ has $\TW_\alpha \tau$.
Please notice that $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.

@@

The subscription $\alpha$ is a transition variable which is called a stage variable in \LMD.
It is used to show the thickness of quoting.
For example, $\TB_\alpha 1$ is a fragment of code which becomes $1$ after run it once and
$\TB_\alpha \TB_\beta 1$ becomes $1$ after run it twice.

@@

% transition abstraction

There are abstraction for transition variables and application for transition abstraction in \LTP.
They looks like $\Lambda\alpha.M$ and $M\ A$, respectively.

% transition application

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bcprules, proof}
\usepackage{fancybox}
\usepackage{mathtools}
\usepackage{float}
\usepackage{xparse}
% \usepackage{ebproof}
\usepackage{lscape}
\usepackage{mdframed}
\usepackage{xspace}

@@

\newcommand{\LTP}{$\lambda^{\triangleright\%}$\xspace}
\newcommand{\LMD}{$\lambda^{\textrm{MD}}$\xspace}
\newcommand{\LLF}{$\lambda^{\textrm{LF}}$\xspace}

@@

In \LTP, quote and unquote are written $\TB_\alpha M$ and $\TBL_\alpha M$, respectively.
The type of $\TB_\alpha M$ is $\TW_\alpha \tau$ when $M$ has $\tau$ type.
The type of $\TBL_\alpha M$ is $\tau$ when $M$ has $\TW_\alpha \tau$.
Please notice that $\TBL_\alpha M$ is well-typed, $M$ has a code type from the typing rule of \LTP.
In addition to normal $\beta$-reduction, there is an reduction rule for unquoted quoted code.
\begin{align*}
	\TBL_\alpha (\TB_\alpha M) \longrightarrow M
\end{align*}
It means when a quoted code fragment is unquoted, it returns back to the original code fragment.
\red{This reduction is called $\longrightarrow_\Lambda$ in \LMD.}

@@

The subscription $\alpha$ is a transition variable which is called a stage variable in \LMD.
It is used to show the thickness of quoting.
For example, $\TB_\alpha (\lambda x:\I.x+10)$ is a fragment of code which becomes $(\lambda x:\I.x+10)$ after run it once and
\red{$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$ becomes $(\lambda x:\I.x+10)$ after run it twice.}

@@

% transition abstraction and application

There are abstraction for transition variables and application for transition abstraction in \LTP.
They looks like $\Lambda\alpha.M$ and $M\ A$, respectively.
A transition abstraction binds a transition variable in a term.
For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
It is only natural there is a rule for transition application in \LTP.
The rule is following.

\begin{align*}
	(\Lambda\alpha.M)\ A \longrightarrow M[\alpha\mapsto A]
\end{align*}

For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ (\beta\gamma)$ reduces to $\TB_{\beta\gamma} (\lambda x:\I.x)$.
\red{Although we can apply any transition to a transition abstraction in \LTP,
we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}
